---
title: "Chapter 6 Homework"
author: "Michelle Mondy"
date: "October 27, 2017"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 6.6 2010 Healthcare Law.

## a) 
False. A confidence interval is constructed to estimate the population proportion, not the sample proportion.

## b) 
True. 95% CI: 46% $\pm$ 3%

## c) 
False. The confidence interval estimates the population porportion, not the sample proportion.

## d) 
False. Since the margin of error at a 95% confidence level is 3%, if we decrease the confidence level, our CI will get smaller. Therefore, the margin of error will be lower than 3%.

# 6.12 Legalization of marijuana, Part I. 

## a) 
sample statistic - it is derived from the sample data

## b) 
95% CI: (0.4524, 0.5076)
```{r}
.48 - (1.96*sqrt((.48*.52)/1259))
.48 + (1.96*sqrt((.48*.52)/1259))
```
We are 95% confident that 45.24% to 50.76% of US residents think marijuana should be legal. 

## c) 
This is true for the data.
Conditions: 
1. the sample observations are independent
2. success-failure condition: both are greater than 10
```{r}
.48*1259
.52*1259
```

## d) 
Based on the CI, the news piece's statement is not justified. The interval does not lie entirely about 50%

# 6.20 Legalize Marijuana, Part II.

1.96*sqrt((.48*.52)/n) <= 0.02 
```{r}
(.48*.52)/(0.02/1.96)^2
```

We would need to survey at least 2398 Americans.

# 6.28 

95% CI for Prop of Californians - Prop of Oregonians: (-0.0175, 0.0015)
```{r}
(.08-.088) - (1.96*sqrt((.08*.92/11545)+(.088*.912)/4691))
(.08-.088) + (1.96*sqrt((.08*.92/11545)+(.088*.912)/4691))
```

We are 95% confident that the proportion of Californians who are sleep deprived are between 1.75% lower and 1.5% higher than the proportion of Oregonians who are sleep deprived.

# 6.44 Barking Deer.

        Woods         Cult. Grass     Dec. Forests       Other         Total
Obs:      4               16              61              345           426
Exp:    20.45           62.62           168.7           174.23

## a) 
Null Hypothesis: Each type of habitat is equally likely. 
Alternative Hypothesis: Some habitats are preferred over others

## b)
Chi-squared goodness of fit test

## c) 
1. Independence: each case is independent of all other cases in the table.
2. sample size/ distribution: Each scenario has at least 5 expected cases.

## d) 
Chi-square test statistic:
```{r}
((4-20.45)^2/20.45)+((16-62.62)^2/62.62)+((61-168.7)^2/168.7)+((345-174.23)^2/174.23)
```
DF = k-1 = 3

```{r}
1-pchisq(284.0762, 3)
```

0 < 0.05 so we reject the null hypothesis. 

Yes, these data provide convincing evidence that barking deer prefer to forage in certain habitats over others.


# 6.48 Coffee and Depression.

       <=1 cup/week      2-6 cups/week    1 cup/day         2-3 cups/day       >=4 cups/day    Total
Yes    670 (627.61)      373 (339.96)    905 (885.49)       564 (631.47)      95 (122.44)      2607
No    11545 (11587.39)   6244 (6277.02)  16329 (16348.51)   11726 (11658.53)  2288 (2260.56)   48132
Tot     12215              6617            17234              12290              2383          50739

Expected counts are in () above. 

## a) 
Chi-square test for two way tables

## b) 
Null hypothesis: The amount of caffeinated coffee consumption is independent of a clinical diagnosis of depression. 
Alternative hypothesis: There is an association between caffeinated coffee consumption and depression.

## c) 
prop of women who suffer from depression
```{r}
2607/50739
```

prop of women who do not suffer from depression
```{r}
48132/50739
```

## d) 
Expected Count for highlighted cell
```{r}
(2607/50739)*6617
```

Contribution to the test statistic
```{r}
(373-339.9854)^2/339.9854
```

## e) 
DF = (2-1)*(5-1)

p-value:
```{r}
1 - pchisq(20.93,4)
```

## f) 
0.00032 < 0.05, therefore we reject the null hypothesis. There is convincing evidence that there is an association between caffeinated coffee consumption and depression.

## e)
Yes, I agree with the statement. It is too early to recommend that women load up on extra coffee. We have only tested for an association, we do not yet know what the relationship is. 