---
title: "Week 2 Assignment"
author: "Michelle Mondy"
date: "September 14, 2017"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 2.6
a) 0
b) 4/36
c) 1/36

## 2.8
a) No, living below the poverty line and speaking a foreign language are not disjoint. 4.2% fall into both categories.
b) 
c) 10.4% live below the poverty line and only speak english
d) 10.4% + 4.2% + 16.5% = 31.1% 
e) 1-0.311 = 68.9%
f) P(LBP) x P(SLOE) =? P(LBP and SLOE)
0.146 x 0.207 = 0.0302 <> 4.2%
No, the events are not independent. 

## 2.20
a) P(Mbl or Fbl) = P(Mbl) + P(Fbl) - P(Mbl and Fbl)
  = (114+108-78)/204 = 144/204 = 70.6%
b) P(Mbl | Fbl) = (78/204)/(108/204) = 72.21%
c) P(Mbr | Fbl) = (19/204)/(108/204) = 17.59%
   P(Mg | Fbl) =  (11/204)/(108/204) = 10.19%
d) Yes, it does appear that the eye colors of male respondents and their partners are independent. 
72.21% + 17.59% + 10.19% = 100% (slightly off from rounding)
The probabilities are conditioned on the same information (Female partner having blue eyes) and they sum to 1. This indicates independence.

## 2.30
a) (28/95)*(67/94) = 21%
b) (72/95)*(28/94) = 22.6%
c) (72/95)*(28/95) = 22.3%
d) When the sample size is only a small fraction of the population, observations are nearly independent even when sampling without replacement.

## 2.38
see PDF/Word doc for solution

##2.44
b)62.2%


```{r}

```




