---
title: "Week 5 Assignment"
author: "Michelle Mondy"
date: "September 30, 2017"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load the required packages
```{r}
library(dplyr)
library(tidyr)
```

## Load the csv file 

```{r}
airline <- read.csv("airline.csv", header=TRUE)
View(airline)
```

## Use the tidyr package to tranform the data into a tidy format. This data can then be used for analysis.
I did this 2 different ways as shown below. 
```{r}
test <- gather(airline, "city", "n", 3:7)
test2 <- spread(test, status, n)

tidy_airline <- airline %>% 
                  gather("city", "n", 3:7) %>% 
                  spread(status, n)
View(tidy_airline)
```

## Perform analysis to compare the arrival delays for the two airlines.
Here I want to look at the total number of delays by airline. I can see that AM West has more total delays.

```{r}
tidy_airline %>% group_by(Airline) %>% 
  summarise(total_delays = sum(delayed))
```

## Additional analysis to compare the ratio of delayed flights to on time flights by airline and city
Here we can still see that AM West has a higher percentage of delays in each city.

```{r}
mutate(tidy_airline, percent_delayed = round((delayed / (delayed+`on time`)) *100, digits=2)) %>% 
 arrange(city, desc(percent_delayed))

```



