---
title: "Movie Rating Assignment"
author: "Michelle Mondy"
date: "September 9, 2017"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Assignment - SQL and R
Choose six recent popular movies.  Ask at least five people that you know (friends,  family,  classmates, imaginary friends) to rate each of these movie that they have seen on a scale of 1 to 5.  Take the results (observations) and store them in a SQL database. Load the information into an R dataframe. 

## Connect to the MySQL database
I created a schema called "movies" which holds the person, movie, and ratings tables.

```{r , echo=FALSE}
pass <- 'sqlpass'
```

```{r}
library(RMySQL)
drv <- dbDriver("MySQL")
con <- dbConnect(drv, user="root", password = pass, dbname="movies", host="localhost")
```


## Query to pull data from the MySQL connection

```{r}
query <- "select * 
          from person a 
          inner join ratings b on a.person_ID = b.person_ID
          inner join movie c on b.movie_ID = c.movie_ID ;"
```


## Load the information into an R dataframe

```{r}
movie_ratings <- fetch(dbSendQuery(con, query))

head(movie_ratings)
```

## Analysis

Which movie had the most reviews?
Note: Null values are present in the rating field when the person did not see the movie. Therefore, the person could not provide a rating.

```{r}
most_reviewed <- "select movie_name, count(rating)
                from ratings b 
                inner join movie c on b.movie_ID = c.movie_ID
                where rating is not null
                group by movie_name
                order by 2 desc limit 1;"
fetch(dbSendQuery(con, most_reviewed))
```



Which movie had the best average rating among the 5 reviewers? 
Note: null values are not included in the average
```{r}
best_rating <- "select movie_name, avg(rating)
                from ratings b 
                inner join movie c on b.movie_ID = c.movie_ID
                group by movie_name
                order by 2 desc limit 1;"
fetch(dbSendQuery(con, best_rating))
```



