---
output:
  pdf_document: default
  html_document: default
---
Load the mushroom data. From the Data Set Description, we should see 8,124 cases and 22 atributes in addition to the class (edible or poisonous).

```{r}
mrdata <- read.csv(url("https://archive.ics.uci.edu/ml/machine-learning-databases/mushroom/agaricus-lepiota.data"), header=FALSE)
dim(mrdata)
```

Let's look at a couple records:
```{r}
head(mrdata)
```

Create a data frame with a subset of the columns in the dataset.You should include the column that indicates edible or poisonous and three or four other columns.  

```{r}
subset <- mrdata[,c("V1","V2","V6","V11","V22","V23")]
head(subset)
dim(subset)
```

You should also add meaningful column names and replace the abbreviations used in the data-for example, in the appropriate column, "e" might become "edible."

```{r}
names(subset) <- c("class","cap-shape","odor","stalk-shape","population","habitat")
names(subset)
head(subset)
```
Replace abbreviations:

```{r}
subset$class <- ifelse(subset$class == 'e', 'edible','poisonous')
library(plyr)
subset$`cap-shape` <- revalue(subset$'cap-shape', c('b'='bell', 'c'='conical', 'x'='convex', 'f'='flat', 'k'='knobbed', 's'='sunken'))
subset$odor <-revalue(subset$odor, c('a'='almond', 'l'='anise','c'='creosote', 'y'='fishy', 'f'='foul', 'm'='musty','n'='none','p'='pungent', 's'='spicy'))
subset$`stalk-shape` <- revalue(subset$`stalk-shape`, c('e'='enlarging','t'='tapering'))
subset$population <- revalue(subset$population, c('a'='abundant','c'='clustered', 'n'='numerous', 's'='scattered','v'='several','y'='solitary'))
subset$habitat <- revalue(subset$habitat, c('g'='grasses','l'='leaves','m'='meadows','p'='paths','u'='urban', 'w'='waste','d'='woods'))
```


Look at this distrubition of levels to ensure revalued.
```{r}
table(subset$`cap-shape`)
table(subset$odor)
table(subset$`stalk-shape`)
table(subset$population)
table(subset$habitat)
```

Save the original and subset datasets to Github

```{r}
save(mrdata, file="mrdata.Rda")
save(subset, file="mrsubdata.Rda")
```

