---
title: "Project 1"
author: "Michelle Mondy"
date: "September 17, 2017"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Load the Rcurl package and the data into R
I had some help from Dave on getting this url to work. I ultimately saved the tournamentinfo.txt link to github which I am referencing below. I chose to exclude headers for now and will reassign them later.

```{r}
library(RCurl)
url <- "https://raw.githubusercontent.com/mmondy/MSDS/master/DATA607/Week%204/tournamentinfo.txt"
data1 <- getURL(url)
data <- read.csv(textConnection(data1), skip=4, header=FALSE, sep="|")
View(data)
```

##Remove every 3rd row
Every third row is a row of dashes so I want to remove that from the output.I consulted StackOverflow for help in finding multiples of 3.

```{r}
rows_in_data= 1:192
every_3_row = (rows_in_data %% 3)==0

new_data <- data[!every_3_row,]
```

##Combine the even and odd rows to one line

```{r}
odd_rows <- new_data[c(TRUE,FALSE),]
even_rows <- new_data[c(FALSE,TRUE),]

even_rows$V11 = c(1:64)
odd_rows$V11 = c(1:64)

combined_data <- merge(even_rows, odd_rows, by="V11")
```

##Keep only the desired columns

```{r}
chess_data <- combined_data[c("V11","V2.y", "V1.x", "V3.y", "V2.x", "V4.y", "V5.y", "V6.y", "V7.y", "V8.y", "V9.y", "V10.y")]
View(chess_data)
```

##Find the Player's Pre Rating using str_split and Regex
I had to go to stackoverflow for help with extracting the second element of each vector using sapply.

```{r}
library(stringr)
rating1 <- sapply(str_split(chess_data$V2.x, "R: "), "[", 2) 
rating2 <- str_extract(rating1, "[[:digit:]]{3,4}")

chess_data$Player_Pre_Rating <- as.integer(rating2)
```

##Find the opponent Pre Rating from the Round variables using regex

```{r}
chess_data$Round1_Opp <- as.integer(str_extract(chess_data$V4.y, "[[:digit:]]{1,2}"))
chess_data$Round2_Opp <- as.integer(str_extract(chess_data$V5.y, "[[:digit:]]{1,2}"))
chess_data$Round3_Opp <- as.integer(str_extract(chess_data$V6.y, "[[:digit:]]{1,2}"))
chess_data$Round4_Opp <- as.integer(str_extract(chess_data$V7.y, "[[:digit:]]{1,2}"))
chess_data$Round5_Opp <- as.integer(str_extract(chess_data$V8.y, "[[:digit:]]{1,2}"))
chess_data$Round6_Opp <- as.integer(str_extract(chess_data$V9.y, "[[:digit:]]{1,2}"))
chess_data$Round7_Opp <- as.integer(str_extract(chess_data$V10.y, "[[:digit:]]{1,2}"))
```


##Create a data frame for cross joining to calculate the Average Pre Chess Rating of Opponents (Avg_Pre_Chess_Rat_Opp)
```{r}
chess_data2 <- chess_data[c("V11","Player_Pre_Rating")]
```

##Join the original chess_data data frame with the data frame above to find the rating of each opponent for each round.

```{r}
library(sqldf)

Round1_Opp_Rating <- sqldf("select b.Player_Pre_Rating from chess_data a left join chess_data2 b on a.Round1_Opp = b.V11")
Round1_Opp_Rating[is.na(Round1_Opp_Rating)]<-0

Round2_Opp_Rating <- sqldf("select b.Player_Pre_Rating from chess_data a left join chess_data2 b on a.Round2_Opp = b.V11")
Round2_Opp_Rating[is.na(Round2_Opp_Rating)]<-0

Round3_Opp_Rating <- sqldf("select b.Player_Pre_Rating from chess_data a left join chess_data2 b on a.Round3_Opp = b.V11")
Round3_Opp_Rating[is.na(Round3_Opp_Rating)]<-0

Round4_Opp_Rating <- sqldf("select b.Player_Pre_Rating from chess_data a left join chess_data2 b on a.Round4_Opp = b.V11")
Round4_Opp_Rating[is.na(Round4_Opp_Rating)]<-0

Round5_Opp_Rating <- sqldf("select b.Player_Pre_Rating from chess_data a left join chess_data2 b on a.Round5_Opp = b.V11")
Round5_Opp_Rating[is.na(Round5_Opp_Rating)]<-0

Round6_Opp_Rating <- sqldf("select b.Player_Pre_Rating from chess_data a left join chess_data2 b on a.Round6_Opp = b.V11")
Round6_Opp_Rating[is.na(Round6_Opp_Rating)]<-0

Round7_Opp_Rating <- sqldf("select b.Player_Pre_Rating from chess_data a left join chess_data2 b on a.Round7_Opp = b.V11")
Round7_Opp_Rating[is.na(Round7_Opp_Rating)]<-0

chess_data$Opp_score <- Round1_Opp_Rating + Round2_Opp_Rating + Round3_Opp_Rating + Round4_Opp_Rating + Round5_Opp_Rating + Round6_Opp_Rating + Round7_Opp_Rating
```

##Determine the number of games played to use in the final calculation for the Avg_Pre_Chess_Rat_Opp

```{r}
game1 <- ifelse(Round1_Opp_Rating == 0, 0, 1)
game2 <- ifelse(Round2_Opp_Rating == 0, 0, 1)
game3 <- ifelse(Round3_Opp_Rating == 0, 0, 1)
game4 <- ifelse(Round4_Opp_Rating == 0, 0, 1)
game5 <- ifelse(Round5_Opp_Rating == 0, 0, 1)
game6 <- ifelse(Round6_Opp_Rating == 0, 0, 1)
game7 <- ifelse(Round7_Opp_Rating == 0, 0, 1)

chess_data$total_games <- game1+game2+game3+game4+game5+game6+game7

chess_data$Avg_Pre_Chess_Rat_Opp <- unlist(round(chess_data$Opp_score/chess_data$total_games, digits=0))
```


##Create final data frame with the just the fields needed and trim the whitespace from Player Name
```{r}
final_data <- chess_data[c("V2.y", "V1.x", "V3.y", "Player_Pre_Rating", "Avg_Pre_Chess_Rat_Opp")]
names(final_data) <- c("Player_Name", "Player_State", "Tot_Num_Points", "Player_Pre_Rating", "Avg_Pre_Chess_Rat_Opp")
final_data$Player_Name <- trimws(final_data$Player_Name, which = "both")
final_data$Player_State <- trimws(final_data$Player_State, which="both")
final_data$Tot_Num_Points <- as.numeric(final_data$Tot_Num_Points)
```

##Write final CSV file

```{r}
write.csv(final_data, file="Project_1_data.csv", row.names=FALSE)
```

