---
title: "Project 2"
author: "Michelle Mondy"
date: "October 7, 2017"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Load the required packages
```{r}
library(RCurl)
library(tidyr)
library(dplyr)
```


#Load the csv file 
I took a snippet of the H1B trend data CSV file from Sarah Wigodsky's discussion board post example. Specifically, I pulled out the Trend of H1B Petitions Filed FY 2007 Through 2017: Beneficiary Industry (Top 30). This shows the number of filings per year by the top 30 industries.

I saved a copy of the original csv to my github site which can be found here:
https://github.com/mmondy/MSDS/blob/master/DATA607/Week%206/h-1b-2007-2017-trend-tables.csv


```{r}
h1b <- data.frame(read.csv(text = getURL("https://raw.githubusercontent.com/mmondy/MSDS/master/DATA607/Week%206/h1bpetitionsindustry.csv"), header = T))
View(h1b)
```

#Transform the data into a tidy format
In order to do this, we need to use the tidyr and dplyr packages to put the data in a more usable format. 
Since the last column shows totals, I am going to drop this column as it will not be accurate once the data is transformed. 

```{r}
tidy_h1b <-  select(h1b, -starts_with("Tot")) %>% gather("Year", "n", 2:12)
head(tidy_h1b)
```

#Analysis
With the data in this long format, I can plot the trend of industries by year. Since there are so many industries, I would like to subset the data for only the top 5.

```{r}
library(sqldf)
#Find the top 5 Industries overall
totals <- tidy_h1b %>% group_by(Industry) %>% summarise(total=sum(n))
arrange(totals, desc(total))

#Another way to do this:
sqldf("select Industry, sum(n) from tidy_h1b group by Industry order by 2 desc limit 5")

top5 <- sqldf("select * from tidy_h1b where Industry in ('Custom Computer Programming Services', 'Computer Systems Design Services', 'Colleges, Universities, and Professional Schools', 'Engineering Services', 'Other Computer Related Services')")
```

Create the charts:
```{r}

library(ggplot2)
ggplot(data=top5, aes(x=Year, y=n, group=Industry, colour=Industry)) +
    geom_line() +
    geom_point()

ggplot(data=top5, aes(x=Year, y=n, fill=Industry)) +
    geom_bar(stat="identity", position=position_dodge(), colour="black")
```

#Conclusions
The beneficiary's Industry for H1B Petitions Filed appear to be largely from Custom Computer Programming Services. Computer Systems Desgin Services appear to be somewhat related and following a similar trend. It's interesting to note that of the top 5 industries, 3-4 are related to computer services. 