---
title: "Week 9 Assignment"
author: "Michelle Mondy"
date: "October 26, 2017"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Overview - Web APIs

The New York Times web site provides a rich set of APIs, including the TimesTags API. For this assignment, I have chose to work with this API which allows you to mine the New York Times tag set. From your query, the response provided is a ranked list of terms. 

I will read in the JSON data from this API for a couple different queries and store the data in R dataframes.

structure:
?query={search-string}&[optional-param1=value1]&[...]&api-key={your-api-key}

The tag dictionaries that are searchable [&filter={dictionary}] include:
(Des)  - descriptive terms
(Geo)  - geographical unit
(Org)  - organizations
(Per)  - personal names

##HTTR 

Using the httr library, I was able to test one of the examples from the Times Tags documentation. This example is a quick query across all dictionaries for the letters 'cel'. 

I have requested an api-key for use of this API which is used throughout the code.

```{r}
#load required package
library(httr)

exampleurl='http://api.nytimes.com/svc/suggest/v1/timestags?query=cel&api-key=7178bcfcb8b24ba3bdf1d837327dfd79'
cel <- GET(exampleurl)

#check the status to be sure the call worked
cel$status_code
#status is 200 which means it worked

#view the content
content(cel, "parse")

```

##Queries from the Times Tags API

I wanted get additional data from the API and test out the different dictionaries and parameters.

```{r}
#here is the base url for the Times Tags API with my API key and a placeholder for the query text ('%s)
baseurl = "http://api.nytimes.com/svc/suggest/v1/timestags%s&api-key=7178bcfcb8b24ba3bdf1d837327dfd79"

#Using sprintf, I am able to paste the query into the baseurl in place of %s

#This query searches for personal names including "Trump" and limits the results to 20.
trump_per = sprintf(baseurl, "?query=Trump&filter=(Per)&max=20")

#This query searches all dictionaries for "Trump" and limits the results to 20.
trump_all = sprintf(baseurl, "?query=Trump&max=20")

#Additional examples
spain = sprintf(baseurl, "?query=spain&filter=(Geo)&max=10")
pres_des= sprintf(baseurl, "?query=pres&filter=(Des)&max=10")
soc_des= sprintf(baseurl, "?query=soc&filter=(Des)&max=10")
hea_org= sprintf(baseurl, "?query=hea&filter=(Org)")
```

##Transform into an R dataframe

The data from the 'cel' example does not look too easy to work with, so I used the jsonlite package on some of the new queries.

```{r}
#load required package
library(jsonlite)

#fromJSON turns the JSON code into an R list. The search criteria is in the first element of the list and the results are in the second element.
fromJSON(trump_all)
#create a dataframe from the second element in the list 
trump <- data.frame(fromJSON(trump_all)[[2]])
names(trump) <- "Tags_incl_'Trump'"
head(trump)
```

##Creating another R dataframe from query results from the API

Here I want to nest functions for cleaner code. I will create a dataframe of the top 200 organizations with 'llc' in the name, based on how frequently they are used in the New York Times.

```{r}
top200 <- data.frame(fromJSON(sprintf(baseurl, "?query=llc&filter=(Org)&max=200"))[[2]])
names(top200) <- "Top200 LLC's"
head(top200)
```

